---
title: "YOQ by Subscale and Diagnosis"
output: html_document
---

```{r library setup}
library(tidyverse)
library(patchwork)
library(rstatix)
```
## Consent Data  

Information related to whether or not a client consented to thier data being used was recorded on a separate survey.  Thus it was important to merge and clean the consent files in order to join them to each individual survey.

```{r consent}
# Read in rds file with aggregrated consent data from consent_clean_PUBLIC.R
consent <- readRDS("rds/consent master list.rds")
# Rename "clientName" to ensure merge is correct
consent <- consent %>% rename(clientName_con = clientName)
```

## YOQ

After data was cleaned ("YOQ clean from orginal data_PUBLIC.R"), missing cases were imputed using linear regression.  Survey information was collected at 4 time points: 1. Day of Admission (DOA), 2. Day of Discharge (DOD), 3. 6 Months post-discharge (MO6), and 4. 1 Year post-discharge (YR1).  Imputation was performed to predict post-discharge values on total scores as well as all subscores.  Cases that were missing either DOA or DOD, and/or both discharge entries were thrown out.

```{r yoq setup}
# Read in YOQ file with imputed values (yoq_imput)
# cleaning process file - YOQ clean from orginal data_PUBLIC.R
# imputation process file - YOQ imputation_PUBLIC.R

## Import YOQ with Imputed Values
yoq_imput_org <- readRDS("rds/updated_imput.rds")

# Merge consent file to YOQ_imput
yoq_imput_con <- merge(yoq_imput_org, consent, by = (c("otClientId", "assignedToRelationship")))

# Remove cases that declined consent and extra name column 
yoq <- yoq_imput_con %>% 
  filter(consent == "Consent") %>% 
  select(-clientName_con)

```

The company was interested in displaying and overall and simple change over time graphic.  Note: all data presented contains some percentage of predicted values based on a linear model.  No difference was found statistically between these predicted values and the orginal data.

```{r}

## Sample Size Tables for legend
YOQ_table <- yoq %>% 
  filter(instance == "DOA") %>% 
  group_by(surveyID, instance) %>% 
  tally() %>% select(-instance)

# Rename instance variable and factor
yoq <- yoq %>% mutate(instance_rename = case_when(
  instance == "DOA" ~ "Admission",
  instance == "DOD" ~ "Discharge", 
  instance == "MO6" ~ "6 Months Post",
  instance == "YR1" ~ "1 Year Post"))

yoq$instance_rename <- factor(yoq$instance_rename, levels = c("Admission", "Discharge", "6 Months Post", "1 Year Post"))


# Plot of all yoq scores
yoq_overall <- ggplot(yoq, aes(color = surveyID)) + 
  stat_summary(aes(x=instance_rename, y=TOTAL), fun = mean, geom = "point") +
  stat_summary(aes(x=instance_rename, y=TOTAL, group = surveyID), 
               fun = mean, geom = "line") +
  labs(title = "Overall YOQ Scores",
       subtitle = "Measure of mental health functioning")+
  scale_color_discrete(labels=paste(YOQ_table$surveyID, YOQ_table$n, sep = " = ")) +
  theme_minimal()+
  theme(legend.position = c(1,1), legend.justification = c(1,1)) + 
  geom_hline(aes(yintercept = 47, 
                 linetype = "Clinical Cutoff"
                 )) +
  scale_linetype_manual(name = "",
                        values = c("Clinical Cutoff" = "dashed")) +
  xlab("Time") + ylab("YOQ Total Score") +
  theme(text = element_text(size = 15)) +
  labs(color = "")
yoq_overall

# Save jpg image
# ggsave("fig/yoq_overall.jpg", yoq_overall, width = 10, height = 7)
```

## YOQ by Subscale  

The YOQ breaks out a clients total score up into 6 different subscales measuring different areas of mental health: 
1. **Intrapersonal Distress (ID)**: measuring anxiety, depression, fearfulness, hopelessness and self-harm  
2. **Somatic (S)**: measuring physical and somatic distress a child or adolescent may be experiencing  
3. **Interpersonal Relations (IR)**: relating to issues in a client's relationship with their family, adults and peers.  
4. **Social Problems (SP)**: assessing troublesome social behavior.  
5. **Behavioral Dysfunction (BD)**: relating to a client's ability to organize tasks, concentrate, handle frustration, etc.  
6. **Critical Items (CI)**: which describes issues which may need immediate inpatient services like suicidal thoughts or self harming behaviors (Burlingame et al., 2019)  

```{r yoq subscale}

YOQ_table <- 

## Make each graph for use individually then bring together
# Scale each plot based on the max and min of that particular subscore

# ID  Intrapersonal Distress
ID <-yoq %>% ggplot(aes(color = surveyID)) + 
  stat_summary(aes(x=instance, y=ID), fun = mean, geom = "point") +
  stat_summary(aes(x=instance, y=ID, group = surveyID), fun = mean, geom = "line", size = 1) +
  geom_abline(intercept = 16, slope = 0, linetype = "dashed") +
  # Max possible of ID is 32, min is 0
  coord_cartesian(ylim = c(0, 32)) +
  labs(subtitle = "Intrapersonal Distress") +
  theme_minimal() +
  theme(legend.position = "none") +
  xlab("Time")

# S Somatic Problems
S <- yoq %>% ggplot(aes(color = surveyID)) + 
  stat_summary(aes(x=instance, y=S), fun = mean, geom = "point") +
  stat_summary(aes(x=instance, y=S, group = surveyID), fun = mean, geom = "line", size = 1) +
  geom_abline(intercept = 6, slope = 0, linetype = "dashed") +
  coord_cartesian(ylim = c(3, 9)) +
  labs(subtitle = "Somatic Problems") +
  theme_minimal() +
  theme(legend.position = "none") +
  xlab("Time")


# IR Interpersonal Relationships
IR <- yoq %>% ggplot(aes(color = surveyID)) + 
  stat_summary(aes(x=instance, y=IR), fun = mean, geom = "point") +
  stat_summary(aes(x=instance, y=IR, group = surveyID), fun = mean, geom = "line", size = 1) +
  geom_abline(intercept = 3, slope = 0, linetype = "dashed") +
  coord_cartesian(ylim = c(-8, 14)) +
  labs(subtitle = "Interpersonal Relationships") +
  theme_minimal() + 
  theme(legend.position = "none") + 
  xlab("Time")

# SP Social Problems
SP <- yoq %>% ggplot(aes(color = surveyID)) + 
  stat_summary(aes(x=instance, y=SP), fun = mean, geom = "point") +
  stat_summary(aes(x=instance, y=SP, group = surveyID), fun = mean, geom = "line", size = 1) +
  geom_abline(intercept = 3, slope = 0, linetype = "dashed") +
  coord_cartesian(ylim = c(-7, 13)) +
  labs(subtitle = "Social Problems") +
  theme_minimal() + 
  theme(legend.position = "none") +
  xlab("Time")

# BD Behavioral Dysfunction
BD <- yoq %>% ggplot(aes(color = surveyID)) + 
  stat_summary(aes(x=instance, y=BD), fun = mean, geom = "point") +
  stat_summary(aes(x=instance, y=BD, group = surveyID), fun = mean, geom = "line", size = 1) +
  geom_abline(intercept = 11, slope = 0, linetype = "dashed") +
  coord_cartesian(ylim = c(1,21)) +
  labs(subtitle = "Behavioral Dysfunction") +
  theme_minimal() + 
  theme(legend.position = "none") +
  xlab("Time")

# CI Critical Items
CI <- yoq %>% ggplot(aes(color = surveyID)) + 
  stat_summary(aes(x=instance, y=CI), fun = mean, geom = "point") +
  stat_summary(aes(x=instance, y=CI, group = surveyID), fun = mean, geom = "line", size = 1) +
  geom_abline(intercept = 6, slope = 0, linetype = "dashed") +
  coord_cartesian(ylim = c(3, 9)) +
  labs(subtitle = "Critical Items", color = "Surveyed Individual") +
  theme_minimal()+
  theme(legend.position = "none") +
  xlab("Time")
  


## Bring them all together 
# YOQ_sub %>% filter(instance=="DOA") %>% filter(subscore=="CI") %>% group_by(surveyID) %>% tally()
YOQ_subscore_grid <- ID + S + IR + SP + BD + CI + plot_annotation(title = "YOQ by Subscale")

YOQ_subscore_grid


# Save jpg
ggsave("fig/YOQ_subscore_grid.jpg", YOQ_subscore_grid, width = 10, height = 7)


```

## By Diagnosis  


```{r yoq_diag, setup}


# Bring in dataset pulled from bestNotes with diagnosis and client ID numbers
diag <- readRDS("rds/bestNotes_diag_wide.rds")

yoq_diag1 <- inner_join(yoq, diag, by = "otClientId")
# This is now a full dataset of all the YOQ scores by diagnosis 
# (repeated ID's due to parents.stus etc)

# Go to long
yoq_diag2 <- gather(yoq_diag1, key = "diag_instance", 
                    value = "diagnosis", 18:27)   # 4840 obs

# Convert to na and remove Remove NA's
yoq_diag3 <- yoq_diag2 %>% 
  mutate_all(na_if, "") %>% 
  mutate_all(na_if, "NONE") %>% 
  mutate_all(na_if, "R/O")


# Change low amounts of data to "other" category in "diagnosis" column
yoq_diag3$diagnosis <- recode(yoq_diag3$diagnosis, life = "other", 
                              neuro = "other", personality = "other", 
                              tech = "other")
# Remove NA's
yoq_diag_cc1 <- yoq_diag3 %>% drop_na(diagnosis)  ## 2488
# Remove duplicates
yoq_diag <- yoq_diag_cc1[!duplicated(yoq_diag_cc1[c(1:14, 17)]),]

# Change to factors
yoq_diag[,c("diagnosis", "diag_instance")] <- lapply(
  yoq_diag[,c("diagnosis", "diag_instance")], factor)
```


```{r}

yoq_diag_plot <- yoq_diag %>% 
  ggplot(aes(color = surveyID)) + 
  stat_summary(aes(x=instance, y=TOTAL), fun = mean, geom = "point") +
  stat_summary(aes(x=instance, y=TOTAL, group = surveyID), fun = mean, geom = "line") +
  geom_abline(intercept = 47, slope = 0, linetype = "dashed") +
  labs(title = "YOQ by Diagnosis", 
       caption = "Students with more than one diagnosis appear multiple times on plots")+ 
  theme_minimal() +
  facet_wrap(~diagnosis)

# Print
yoq_diag_plot


# Save jpg
ggsave("fig/yoq_diag_plot.jpg", yoq_diag_plot, width = 10, height = 7)


```
Note: sample sizes did not end up being large enough to draw conclusive findings from this analysis.  

## YOQ by post discharge placement  

```{r}
## Aftercare data setup ----

AQD <- readRDS("rds/AQD_clean.rds")
PQPD_19.1 <- readRDS("rds/PQPD_19.rds")

# Recode the residency options
AQD$residency_recode <- as.factor(recode(AQD$residency, 
                         ACADEMIC_BOARDING = "boarding", 
                         ALONE = "home",
                         FATHER = "home",
                         MOTHER = "home", 
                         PARENTS = "home", 
                         RESIDENT_TREAT = "boarding", 
                         OTHER = "other",
                         ROOMMATE = "home",
                         TBS = "boarding")) 
# simplify data frame
AQD_res <- AQD %>% select(CID:LastName, DOB, residency, residency_recode) %>% 
  na.omit()


# And for PQPD
# Relabel aftercare setting to transistion 
PQPD_res <- PQPD_19.1 %>% rename(residency = Q2a) %>% 
  mutate(residency_recode = recode(residency, A = "home", B = "home", 
                            C = "boarding", D = "boarding",
                            E = "other", `F` = "other", 
                            G = "home", H = "other", I = "other")) %>% 
  filter(residency != "Currently, where is your child living?") %>% 
  select(CID:LastName, DOB, residency, residency_recode) %>% 
  mutate_all(na_if, "") %>% drop_na(residency_recode)

# Bind objects together
res <- rbind(PQPD_res, AQD_res)

# Remove duplicates and restructure dates
res <- res[!duplicated(res["CID"]),]
res$DOB <- as.Date(res$DOB, "%m/%d/%Y")

# This survey only has the CID number, so we need to add otClientId number
master_Id <- readRDS("rds/master list of names and id.rds")


# merge this to res
res_otId <- merge(res, master_Id, by.x = "CID", by.y = "remoteClientId")


# MERGE YOQ Scores to residency status ----

yoq_res <- merge(yoq, res_otId, by = "otClientId")
# yoq_res <- yoq_res %>% select(CID, clientName, FirstName, LastName, 
#                               surveyID:residency_recode)
# 

## Aftercare Plot ----



# Recode residency
yoq_res$residency_recode <- recode(yoq_res$residency_recode,
                                    after_care = "boarding")


# By PARENT VS STUDENT
par.tally <- yoq_res %>% 
  filter(surveyID == "Parent", residency_recode != "other") %>% 
  group_by(residency_recode) %>% filter(instance == "DOA") %>% tally()

par.place.plot <- yoq_res %>% 
  filter(surveyID == "Parent", residency_recode != "other") %>% 
  ggplot(aes(color = residency_recode)) + 
  stat_summary(aes(x=instance, y=TOTAL), fun = mean, geom = "point") +
  stat_summary(aes(x=instance, y=TOTAL, group = residency_recode), 
               fun = mean, geom = "line") +
  geom_abline(intercept = 46, slope = 0, 
              linetype = "dashed") +
  labs(subtitle = "Parents",
       caption = "Parent Cutoff = 46",
       color = "Residency")+
  coord_cartesian(ylim = c(30, 105))+
  scale_color_discrete(labels=paste(par.tally$residency_recode, 
                                    par.tally$n, sep = " = ")) +
  theme_minimal() +
  theme(legend.position = c(1,1), legend.justification = c(1,1))


## STUDENT PLACEMENT PLOT
stu.tally <- yoq_res %>% 
  filter(surveyID == "Student", residency_recode != "other") %>% 
  group_by(residency_recode) %>% filter(instance == "DOA") %>% tally()

stu.place.plot <- yoq_res %>% 
  filter(surveyID == "Student", residency_recode != "other") %>% 
  ggplot(aes(color = residency_recode)) + 
  stat_summary(aes(x=instance, y=TOTAL), fun = mean, geom = "point") +
  stat_summary(aes(x=instance, y=TOTAL, group = residency_recode), 
               fun = mean, geom = "line") +
  geom_abline(intercept = 46, slope = 0, 
              linetype = "dashed") +
  labs(title = "YOQ Scores by Post-Discharge Residency",
       subtitle = "Students",
       caption = "Student Cutoff = 47", 
       color = "Residency")+
  coord_cartesian(ylim = c(30, 105))+
  scale_color_discrete(labels=paste(stu.tally$residency_recode, 
                                    stu.tally$n, sep = " = ")) +
  theme_minimal() +
  theme(legend.position = c(1,1), legend.justification = c(1,1))

yoq_post_dis <- stu.place.plot + par.place.plot

# Print
yoq_post_dis

# Save jpg
ggsave("fig/yoq_post_dis.jpg", yoq_post_dis, width = 10, height = 7)

```


```{r}
yoq_res %>% 
  filter(residency_recode != "other") %>% 
  group_by(instance, surveyID) %>% 
  t_test(TOTAL ~ residency_recode) %>%
  adjust_pvalue(method = "BH") %>% 
  add_significance()
```

No statistical difference was shown between student scores but there was a statistical difference for parent scores at all points other than admission suggesting that parents who bring their child home at discharge rate them as doing better but at 6 months and a year out rate them as actually doing a bit worse.

**There's gotta be a better cooler way to think about and visualize that, maybe even just bolding or highlighting in some way the statistially significant differnt values?**




